Zero-Knowledge Credentials for Smart Contracts

### 2019-01-16 paper/paper.tex

\subsection{Prior Work}
Identity systems for public blockchains have been proposed before in the form of
serivces like Civic and Uport, wherein users can acquire attestations from
trusted issuers about facets of their identity (name, age, country of origin,
etc). These services promise ``anonymous'' attestation, but are
\textit{linkable}, i.e.\ multiple attestations by the same user are trivially
identifiable, and \textit{pseudonymous}, i.e.\ attestations are
linked to a pseudonym that is known by the credential issuer. If a credential
issuer leaks their records, then all past activity by a user is deanonymized.

@@

\subsection{The ZKID Service}

\subsubsection{libsnark}

\subsubsection{JSON RPC}

@@

\subsection{dApp Framework and Credential-Enabled Contracts}

Add some Introduction here

@@

@@

\section{Future Work}

\section{Conclusion}

>>>>

\subsection{Prior Work}
Identity systems for public blockchains have been proposed before in the form of
serivces like Civic\cite{CivicSecureIdentity} and Uport\cite{braendgaardDifferentApproachesEthereum2018}, wherein users can acquire attestations from
trusted issuers about facets of their identity (name, age, country of origin,
etc). These services promise ``anonymous'' attestation, but are
\textit{linkable}, i.e.\ multiple attestations by the same user are trivially
identifiable, and \textit{pseudonymous}, i.e.\ attestations are
linked to a pseudonym that is known by the credential issuer. If a credential
issuer leaks their records, then all past activity by a user is deanonymized.

@@

\subsection{The ZKID Service}
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.5]{issuing}\vspace{40pt}
  \includegraphics[scale=0.5]{verifying}
  \caption{ZKID Service}
\end{figure}
\subsubsection{JSON RPC}

@@

@@

Deployment of our contract takes $3.6$ million gas, and a single execution of
the verifier requires $1.79$ million. At current prices this is about $0.01432$
ETH or $\$10.50$. Proving time for a tree dept of $32$ is 43.2 seconds. We feel
that these are reasonable enough for use, but could certainly be improved as
discussed below. Proving time scales linearly with the depth of the merkle tree,
while verification cost is constant.

@@

\section{Future Work}
Currently the contract does not make use of the preprocessed verifier that
libsnark provides, which would allow us to remove 2 pairing checks at the cost
of several EC group operations. Additionally, Zcash is developing a new zkSNARK
system on a more efficient curve called JubJub\cite{ZcashJubjub} that allows fixed-base
exponentiation for efficient EC operations in
circuits, allowing efficient CRHs.

\section{Acknowledgements}
Huge thanks to Ian Miers for helping set us on the right path and formalizing
the properties that an anonymous credential scheme should have.
